---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# exponential (Package Description)

<!-- badges: start -->
<!-- badges: end -->

The `exponential()` function in this eponymously named package computes the exponential of a number, vector of numbers, or a (numeric) variable in a tibble. This is done recursively, via a truncated approximation of the Taylor-series definition of the exponential function. This function can be used to reverse logarithmic transformations of numerical variables, as shown in the last example below.

## Installation

You can install the development version of exponential like so:

``` r
# install.packages("devtools") # only if not already installed
devtools::install_github("jsa378/exponential", ref = "0.1.0")
```

## Examples

These are basic examples of the use of the `exponential()` function. We apply `exponential()` to a single number, a vector of numbers, a vector of numbers and `NA` values, and a numerical variable in a tibble.

```{r example}
library(exponential)

exponential(1) # exponentiate a number

exponential(c(1, 2)) # exponentiate a vector of numbers

exponential(c(3, NA)) # the function accepts NA inputs

# Next, we apply the function to a numerical variable
# in a tibble

# We use a dataset of trees from the datateachr package,
# and apply exponential to the logarithm of the tree diameters
library(datateachr)
library(dplyr)

# Filter out observations with 0 diameter,
# arrange by diameter (decreasing),
# select diameter column,
# create log_diam and exp_log_diam
log_diam_dataset <- vancouver_trees |>
  filter(diameter > 0) |>
  arrange(desc(diameter)) |>
  select(diameter) |>
  mutate(
    log_diam = log(diameter),
    exp_log_diam = exponential(log_diam)
  )

# View log_diam_dataset
log_diam_dataset

# Check that the diameter
# and exp_log_diameter columns
# are equal
tibble_1 <- log_diam_dataset |> select(diameter)
tibble_2 <- log_diam_dataset |> select(exp_log_diam)
all.equal(tibble_1, tibble_2, check.attributes = FALSE)
```

For further guidance regarding how to use the `exponential()` function, please install the package and see the `exponential()` function documentation.
